Fitting parametric univariate distributions to non censored or censored data using the R \texttt{fitdistrplus} package

### 2012-01-21 inst/doc/intro2fitdistrplus.Rnw
add scaling problem example, specify encoding for the vignette, update news.

@@

% A changer en cas de mise à jour de fitdistrplus !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
This paper reviews the various features of version 0.3-0 of \texttt{fitdistrplus}. The package
is available from the Comprehensive R Archive Network at \url{http://cran.r-project.org/package=fitdistrplus}.
The development version of the package is located at R-forge as one the packages of the 
project ``Risk Assessment with R''
(\url{http://r-forge.r-project.org/projects/riskassessment/})
The following command will load the package.
<<results=hide>>=
library(fitdistrplus)
@

@@

Function \texttt{fitdist} returns the results of the fit of any parametric distribution 
to a data set as an S3 class object that may be easily printed, 
summarized or plotted (see Figure~\ref{fitgamma} in Section~\ref{GOF plots}). 
The parametric distribution must be a classically defined R distributions,
with at least d, p and q functions respectively for the density cdf and quantile functions
(for example \texttt{dnorm}, \texttt{pnorm} and \texttt{qnorm} for the normal distribution).
The name of the fitted distribution is specified in the first argument by its classical 
abbreviation used as the second part of d, p and q functions (for example ``norm''
for the normal distribution. Numerical results returned by Function \texttt{fitdist} are 
parameter estimates with estimated standard errors computed from the estimate
of the Hessian matrix at the maximum likelihood solution, correlation matrix
between parameter estimates, the loglikelihood, the Akaïke and the Schwarz information criteria 
(so called AIC and BIC).
<<echo = TRUE,fig = FALSE>>=
fw <- fitdist(groundbeef$serving,"weibull")
print(fw)
summary(fw)
@

@@

In such a plot, data may be represented in a log scale when required, by just fixing the argument
\texttt{xlogscale} to \texttt{TRUE} in the call to \texttt{cdfcomp}.
% Ajouter ex endosulfan avec la bibliothèque actuar !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
% mais comment faire dans la vignette : indiquer que fitdistrplus nécessite actuar????????????????????????????

>>>>

% accents 8 bits dans le fichier
%\usepackage[applemac]{inputenc} %MAC encoding
%\usepackage[utf8]{inputenc} %UNIX encoding
\usepackage[ansinew]{inputenc} %WINDOWS encoding

@@

% A changer en cas de mise ‡ jour de fitdistrplus !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
This paper reviews the various features of version 0.3-0 of \texttt{fitdistrplus}. The package
is available from the Comprehensive R Archive Network at \url{http://cran.r-project.org/package=fitdistrplus}.
The development version of the package is located at R-forge as one the packages of the 
project ``Risk Assessment with R''
(\url{http://r-forge.r-project.org/projects/riskassessment/})
The following command will load the package.
<<results=hide>>=
library(fitdistrplus)
@

@@

Function \texttt{fitdist} returns the results of the fit of any parametric distribution 
to a data set as an S3 class object that may be easily printed, 
summarized or plotted (see Figure~\ref{fitgamma} in Section~\ref{GOF plots}). 
The parametric distribution must be a classically defined R distributions,
with at least d, p and q functions respectively for the density cdf and quantile functions
(for example \texttt{dnorm}, \texttt{pnorm} and \texttt{qnorm} for the normal distribution).
The name of the fitted distribution is specified in the first argument by its classical 
abbreviation used as the second part of d, p and q functions (for example ``norm''
for the normal distribution. Numerical results returned by Function \texttt{fitdist} are 
parameter estimates with estimated standard errors computed from the estimate
of the Hessian matrix at the maximum likelihood solution, correlation matrix
between parameter estimates, the loglikelihood, the AkaÔke and the Schwarz information criteria 
(so called AIC and BIC).
<<echo = TRUE,fig = FALSE>>=
fw <- fitdist(groundbeef$serving,"weibull")
print(fw)
summary(fw)
@

@@

In such a plot, data may be represented in a log scale when required, by just fixing the argument
\texttt{xlogscale} to \texttt{TRUE} in the call to \texttt{cdfcomp}.
% Ajouter ex endosulfan avec la bibliothËque actuar !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
% mais comment faire dans la vignette : indiquer que fitdistrplus nÈcessite actuar????????????????????????????
